---
title: "R Notebook"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,get_dataset}
#subj_count = 3
subj_num = 0

dataset <- data.frame()

path_data <- "resource/res_analyz_spr_10/"

best_value <- as.numeric(readLines(file.path(path_data,"ColorOptimalLength.txt"), 30))

dirsAll <- list.dirs(path =file.path(path_data, "TSP_spr_19/colored") , full.names = TRUE, recursive = TRUE) #all subfolders


dirsAll <- grep("results", dirsAll, value = TRUE) #all subfolders that the result folder is there
#dirsAll




subj_count <- length(dirsAll) #
res_tbl <- matrix(0, nrow = 30, ncol = subj_count)
res_tble_err <- matrix(0, nrow = 30, ncol = subj_count)
res_err_time_ordered <- matrix(0, nrow = 30, ncol = subj_count)
res_tbl_time_ordered <- matrix(0, nrow = 30, ncol = subj_count)
file_time_number_all_subj <- matrix(0,subj_count,30)
#all result files for each subject one by one
counter_order <- 0
for(folder in dirsAll[1:length(dirsAll)]) {
  
    #-------------------
    #order of files by their creation time
    details = file.info(list.files(folder, pattern="*.tspx", full.names=TRUE))
    details = details[with(details, order(as.POSIXct(mtime))), ]
    files_time_ordered = rownames(details)
    # print(details)
    # finding the number of the file
    match <- gregexpr("_|-", files_time_ordered)
    
    match <- as.numeric(unlist(regmatches(files_time_ordered, gregexpr("[[:digit:]]+", files_time_ordered))))
    #FN <- as.numeric(unlist(match))
    file_time_number<-match[c(rep(FALSE,(length(match)/30)-1),TRUE)]
    print(file_time_number) # order of maps for each subject
    counter_order = counter_order +1
    file_time_number_all_subj[counter_order,] <- file_time_number # order of maps for all subjects
    #--------------------
  
  
    subj_num = subj_num + 1
    counter =0
    #filenames <- list.files(paste(folder+, pattern="*.tspx", full.names=TRUE)
    while (counter < 30){
        file <- paste(folder,"/TSPMap_RandomPoints_Color_SwitchCost_",toString(counter),"-CollectedTour.tspx",sep = "")
        file
        counter=counter+1
        fMap <- readLines(file,58)
        #---------------
        tourL = 0
        #-----
        #extracting points and color from each tour file
        matches <- regmatches(fMap, gregexpr("[[:digit:]]+", fMap))
        fN <- as.numeric(unlist(matches))
        fNum<-fN[6:length(fN)]
        coord <- matrix(fNum,byrow = TRUE, 50, 3)
        #calculating distance
        dis_mat <- as.matrix(dist(coord, method = "euclidean"))
        #---------------
        #tourL <- sum(diag(dis_mat[2:49,1:49]))#single color calculation 
        #tourL
        #---------------
        #for colored
        
        #---
        #goal: finding non_euclidean point changes and doubling those distances
        shifted_coord <- coord[,3]
        shifted_coord[2:50] <- coord[1:49,3]
        nonEuc_edge <- which(coord[,3] != shifted_coord)#finding the indices of change of color # the 1st and last one and the second are exceptions
        
        #---
        #applying non euc distances to the distance matrix
        dis_nonEuc <- dis_mat
        dis_nonEuc[nonEuc_edge,nonEuc_edge-1] <- 2*dis_nonEuc[nonEuc_edge,nonEuc_edge-1] #applying non_euc distances
        
        #---
        #distance between last point to first point
        last_to_first<- (2 - as.numeric( coord[50,3] == coord[1,3]))* dist(matrix (c (coord[50,1], coord[50,2], coord[1,1], coord[1,2]), nrow = 2, ncol = 2, byrow = TRUE))#the first paranthesis is for checking if the last edge is euclidean or not
        
        #---
        #tour calculation
        tourL <- sum(diag(dis_nonEuc[2:50,1:49])) + last_to_first
        #print(tourL)
        #print(file)
        #write(tourL, file = "C:/Users/zsajedin/Desktop/data.txt",
        #  ncolumns = 1,
        #  append = TRUE, sep = "\n")
        res_tbl [counter, subj_num] <- tourL # calculating tour for map number i
        res_tble_err[counter, subj_num] <- (tourL-best_value[counter])/best_value[counter]# error of map number i
        res_err_time_ordered[which(file_time_number[1:30]==counter-1), subj_num] <-  res_tble_err[counter, subj_num]# error of map number i but puting that in the order that it appeard.
        res_tbl_time_ordered[which(file_time_number[1:30]==counter-1), subj_num] <-  res_tbl[counter, subj_num]# total length of map number i but puting that in the order that it appeard.
    #
    }
}

res_tble_analyzed <- as.data.frame( res_tbl_time_ordered)


res_tble_analyzed [nrow(res_tbl)+1,] <- colMeans (res_tbl_time_ordered)
dim(res_tble_analyzed)
res_tble_analyzed [1:nrow(res_tbl_time_ordered),ncol(res_tbl_time_ordered)+1] <- rowMeans(res_tbl_time_ordered)#adding mean of each map and each subject
dim(res_tble_analyzed)


blocked_res <- matrix(res_tbl_time_ordered,nrow = 6, byrow = TRUE)
#blocked_res
#res_tble_analyzed
#res_tble_analyzed [,ncol(res_tble_analyzed)+1] <- mean(res_tble_analyzed)
#mean(res_tble_analyzed)

write.csv (res_tble_analyzed, file.path(path_data, "output/subjTours.csv"))
write.csv (res_err_time_ordered, file.path(path_data, "output/TSP_color_2019_res.csv"))

#
```

```{r}
library(XML)

get_map_score <- function() {
  path_data <- "resource/res_analyz_spr_10/"
  best_value <- as.numeric(readLines(file.path(path_data,"ColorOptimalLength.txt"), 30))
  best_value
}

# 32 subjects
get_subject_dir_map <- function() {
  path_data <- "resource/res_analyz_spr_10/TSP_spr_19/colored"
  dirsAll <- list.dirs(path =file.path(path_data) , full.names = TRUE, recursive = TRUE) 
  dirsAll <- grep("results", dirsAll, value = TRUE)
  subj_count <- length(dirsAll) #
  dirsAll
}
map_score <- get_map_score()
subject_dir_map <- get_subject_dir_map()

get_distance_from_two_record <- function(point1, point2) {
  distance <- sqrt((point1-point2)[1]^2 + (point1-point2)[2]^2)
  if(point1[3] != point2[3]) {
      distance <- 2 * distance
  }
  distance
}

get_real_record <- function(map_id, subject_id, subject_dir_map) {
  
  file <- paste(subject_dir_map[subject_id],"/TSPMap_RandomPoints_Color_SwitchCost_", toString(map_id-1),"-CollectedTour.tspx",sep = "")
  file
  
  file_content = readChar(file, file.info(file)$size)
    

  file.info(file)
  details = details[with(details, order(as.POSIXct(mtime))), ]
  details

  tmp_data <- NULL
  first_data <- NULL
  distance_all <- 0
  count <- 0
  for(city in xmlChildren(xmlChildren(xmlChildren(xmlRoot(xmlParse(file_content)))$Tours)$Tour)) {
    count <- count + 1

    city_attr <- xmlAttrs(city)
    data<-c(as.numeric(city_attr['x']), as.numeric(city_attr['y']), as.numeric(city_attr['group']))
    
    if(is.null(first_data)) {
      first_data <- data
    }

    if (count != 1) {
      distance_all <- distance_all + get_distance_from_two_record(tmp_data, data)
      if (count == 50) {
        distance_all <- distance_all + get_distance_from_two_record(first_data, data)
      } # if
    }# if
    tmp_data <- data
  } # for all cities

  distance_all
}

experiment_table <- data.frame()
for(subject_id in 1:27) {
  for(map_id in 1:30) {
    real_score <- get_real_record(map_id, subject_id, subject_dir_map)
    best_score <- map_score[map_id]
    err_ratio <- (real_score-best_score)/best_score
    record <- data.frame(map_id, subject_id, real_score, best_score, err_ratio)
    experiment_table <- rbind(experiment_table, record)
  }
}
experiment_table
```



```{r}
library(ggplot2)



#df2 <- data_summary(res_err_time_ordered[,4])



#Analyzing data
#mean_col <- ncol(res_err_time_ordered)

mean_of_5 <- data.frame(1:6,0)
std <- data.frame(1:6,0)
for (nn in 1:6){
mean_of_5 [nn] <- mean(res_err_time_ordered[((nn*5)-5+1):(nn*5),])
std[nn] <- sd (res_err_time_ordered[((nn*5)-5+1):(nn*5),])/sqrt(length(res_err_time_ordered[((nn*5)-5+1):(nn*5),]))
}



ggplot( 
  data = mean_of_5,mapping = aes( x= 1:6 ,y = mean_of_5[,2])) + 
   geom_path(size=1) + geom_errorbar(aes(ymin=(mean_of_5[,2]-std[,2]), ymax=(mean_of_5[,2]+std[,2])), width=.2,
                 position=position_dodge(0.05)) +coord_cartesian(xlim=c(1, 6),ylim=c(.15, .25)) +ylab("Error") +xlab("Blocks") 

blc <- c("bl1","bl2","bl3","bl4","bl5","bl6")

fit <- aov(mean_of_5[,2] ~ blc, data=mean_of_5)


#sign test
binom.test(18, 32, p = 0.5, alternative = "two.sided", conf.level = 0.95)



```

```{r}

#plotting first 5-6 trials only
library(ggplot2)
library(tidyr)


#df2 <- data_summary(res_err_time_ordered[,4])



#Analyzing data
#mean_col <- ncol(res_err_time_ordered)

mean_of_5 <- data.frame(1:6,0)
std <- data.frame(1:6,0)

mean_of_5 [1:6] <- mean(res_err_time_ordered[1:(nn*5),])
std[1:6] <- sd (res_err_time_ordered[1:(nn*5),])/sqrt(length(res_err_time_ordered[1:(nn*5),]))



mean_of_5 <- data.frame(1:6,mean_of_5)
res_err_time_ordered[1:(nn*5),]

ggplot( 
  data = mean_of_5,mapping = aes( x= 1:6 ,y = mean_of_5[,2])) + 
   geom_path(size=1) + geom_errorbar(aes(ymin=(mean_of_5[,2]-std[,2]), ymax=(mean_of_5[,2]+std[,2])), width=.2,
                 position=position_dodge(0.05)) +coord_cartesian(xlim=c(1, 6),ylim=c(.1, .3)) +ylab("Error") +xlab("Blocks") 

blc <- c("bl1","bl2","bl3","bl4","bl5","bl6")

fit <- aov(mean_of_5[,2] ~ blc, data=mean_of_5)


```

```{r}

mat <- matrix(c(2, 4, 3, 1, 5, 7), nrow=3, ncol=2)
colnames(mat) <- c("col1","col2")
rownames(mat) <- c("row1","row2","row3")
library(reshape)
library(ggvis)
melt(mat)


res_df <- data.frame("bl" = rep(1:6,times=32), "subj" = c( rep(1:6,times=32)) )
?rep
(res_err_time_ordered)
res_df_gather <- gather(res_df, )
col(res_err_time_ordered)


plt<- ggvis(res_err_time_ordered,x=~row(res_err_time_ordered),y=1) %>%  layer_lines()

plt



?as.data.frame



gather(as.data.frame(res_err_time_ordered), key = "subj", value = "err", 1:32)

```

```{r}

library(ggvis)
library(dplyr)

mean_of_5_per_subj <- data.frame(1:6,0)
std_per_subj <- data.frame(1:6,0)
for (mm in 1:32){
  for (nn in 1:6){
  mean_of_5_per_subj [nn,mm] <- mean(res_err_time_ordered[((nn*5)-5+1):(nn*5),mm])
  std_per_subj[nn,mm] <- sd (res_err_time_ordered[((nn*5)-5+1):(nn*5),mm])/sqrt(length(res_err_time_ordered[((nn*5)-5+1):(nn*5),mm]))
  }
}
colnames(mean_of_5_per_subj) <- c(1:32)

res_gather <- gather(as.data.frame(mean_of_5_per_subj), key = "subj", value = "err", 1:32)

res_gather$bl <- rep(c(1:6),32)


plt<- res_gather%>% ggvis(~subj,~err,stroke = ~bl,fill=~bl) %>% group_by(bl) %>% 
        layer_points() %>% scale_numeric("stroke", range = c("yellow", "red"))%>% scale_numeric("fill", range = c("yellow", "red"))

plt

res_gather[1,2]


plt<- res_gather[61:120,]%>% ggvis(~bl,~err,stroke = ~subj) %>% group_by(subj) %>% 
        layer_lines(strokeWidth := 2)  %>% add_axis("x", ticks = 6)

plt

res_gather$ID <- c(1:(32*6))

plt<- res_gather%>% ggvis(~ID,~err,stroke = ~subj) %>% group_by(subj) %>% 
        layer_lines(strokeWidth := 2)  %>% add_axis("x", ticks = (32*6))

plt
```

```{r}

file_time_number_all_subj

res_err_time_ordered

mean_map <- matrix (0,30,30)



res_err_time_ordered_transpose <- matrix (0, 32,30) 
res_err_time_ordered_transpose <- t(res_err_time_ordered)
file_time_number_all_subj_no_zero <- file_time_number_all_subj + 1
for (row_map in 1:30){
  for (col_trial in 1:30){
    mean_map[row_map,col_trial] <- mean(res_err_time_ordered_transpose[which(file_time_number_all_subj_no_zero[,col_trial]== row_map),col_trial])
    
  }
}



mean_map_5_per_map <- matrix(0,30,6)
for (mm in 1:30){
  for (nn in 1:6){
  mean_map_5_per_map [mm,nn] <- mean(mean_map[mm,((nn*5)-5+1):(nn*5)], na.rm=TRUE)
  }
}


mean_map_5_per_map_df  <- gather(as.data.frame(t(mean_map_5_per_map)), key = "map", value = "err", 1:30)
mean_map_5_per_map_df$bl <- rep(1:6,30)
mean_map_5_per_map_df$ID <- 1:180

plt<- mean_map_5_per_map_df%>% ggvis(~map,~err,stroke = ~bl,fill=~bl) %>% group_by(bl) %>% 
        layer_points() %>% scale_numeric("stroke", range = c("yellow", "red"))%>% scale_numeric("fill", range = c("yellow", "red"))

plt

res_gather[1,2]


plt<- res_gather[61:120,]%>% ggvis(~bl,~err,stroke = ~subj) %>% group_by(subj) %>% 
        layer_lines(strokeWidth := 2)  %>% add_axis("x", ticks = 6)

plt


res_gather$ID <- c(1:(32*6))

plt<- mean_map_5_per_map_df%>% ggvis(~ID,~err,stroke = ~map) %>% group_by(map) %>% 
        layer_lines(strokeWidth := 2)  %>% add_axis("x", ticks = (32*6))

plt
```

```{r}

```

```{r}

```

```{r}

```

```{r}
#finding what the random number was for each tour from the availabe points




#First finding the original order of maps
subj_num = 0


#filenames <- list.files("C:/Users/zsajedin/Desktop/results", pattern="*.tspx", full.names=TRUE)
#tsp_result_colored_feb_25_2019
dirsAll <- list.dirs(path ="C:/Users/zsajedin/Desktop/test" ,full.names = TRUE, recursive = TRUE) #all subfolders

dirsAll <- grep("results", dirsAll, value = TRUE) #all subfolders
dirsAll

res_tbl_Original <- matrix(0, nrow = 30, ncol = 50) # saving  the orderd map



#reading each map file
for(folder in dirsAll[1:length(dirsAll)]){
    subj_num = subj_num + 1
    counter =0
    #filenames <- list.files(paste(folder+, pattern="*.tspx", full.names=TRUE)
    while (counter< 30 ){
        file <- paste(folder,"/TSPMap_RandomPoints_Color_SwitchCost_",toString(counter),".MapXml",sep = "")
        file
        counter=counter+1
        fMap <- readLines(file,58)
        #---------------
        tourL = 0
        #-----
        #extracting points and color from each tour file
        matches <- regmatches(fMap, gregexpr("[[:digit:]]+", fMap))
        fN <- as.numeric(unlist(matches))
        fNum<-fN[5:length(fN)]#5 because we do not need the first 5 numbers in xmlmap file
        coord <- matrix(fNum,byrow = TRUE ,50,3)


        #comparing them with 30maps
        coord_ordered = coord[order(coord[,1])]
        
         res_tbl_Original[counter,1:50] <- coord_ordered[1:50]
       

  #saving the matched map


}
}


#-------------------------------------------
#Second finding the random order of maps for each subject



#First finding the original order of maps
subj_num = 0


#filenames <- list.files("C:/Users/zsajedin/Desktop/results", pattern="*.tspx", full.names=TRUE)
#tsp_result_colored_feb_25_2019
dirsAll <- list.dirs(path ="C:/Users/zsajedin/Desktop/test" ,full.names = TRUE, recursive = TRUE) #all subfolders
subj_count <- length(dirsAll)-1 #-1 bcz root is

dirsAll <- grep(pattern = "results", dirsAll, value = TRUE) #all subfolders
dirsAll

res_tbl <- matrix(0, nrow = 30, ncol = 50) # saving  the orderd map



#reading each map file
for(folder in dirsAll[1:length(dirsAll)]){
    subj_num = subj_num + 1
    counter =0
    #filenames <- list.files(paste(folder+, pattern="*.tspx", full.names=TRUE)
    while (counter< 30 ){
        file <- paste(folder,"/TSPMap_RandomPoints_Color_SwitchCost_",toString(counter),".mapxml",sep = "")
        file
        counter=counter+1
        fMap <- readLines(file,58)
        #---------------
        tourL = 0
        #-----
        #extracting points and color from each tour file
        matches <- regmatches(fMap, gregexpr("[[:digit:]]+", fMap))
        fN <- as.numeric(unlist(matches))
        fNum<-fN[6:length(fN)]
        coord <- matrix(fNum,byrow = TRUE ,50,3)


        #comparing them with 30maps
        coord_ordered <- coord[order(coord[1:50,3])]
        
       res_tbl[counter,1:50] <- coord_ordered[1:50]
       map_order <- 30:59
       
       for (mm in 1:30){
         map_order[mm] <- which(apply(res_tbl_Original, 1, function(x) all(x == res_tbl[mm,1:50])))

         #map_order[mm] <- which(res_tbl_Original==res_tbl_Original[mm,1:50])
         #map_order[mm] <- which(apply(res_tbl_Original[1:30,1:50], 1, function(x) all.equal(x[1:50], res_tbl[mm,1:50])) == "TRUE")
       }
       write(map_order, file = paste(folder,"/rnd.txt"),sep = "")
       
       
  #saving the matched map


}
}

```

```{r}
subj_num = 0


#filenames <- list.files("C:/Users/zsajedin/Desktop/results", pattern="*.tspx", full.names=TRUE)
#tsp_result_colored_feb_25_2019
dirsAll <- list.dirs(path ="C:/Users/zsajedin/Desktop/test0" ,full.names = TRUE, recursive = TRUE) #all subfolders

dirsAll <- grep("results", dirsAll, value = TRUE) #all subfolders
dirsAll

res_tbl <- matrix(0, nrow = 30, ncol = 50) # saving  the orderd map



#reading each map file




for(folder in dirsAll[1:length(dirsAll)]){
    subj_num = subj_num + 1
    counter =0
    #filenames <- list.files(paste(folder+, pattern="*.tspx", full.names=TRUE)
    #-------------------
    #ordering files by their creation time
    details = file.info(list.files(folder, pattern="*.tspx", full.names=TRUE))
    details = details[with(details, order(as.POSIXct(mtime))), ]
    files_time_ordered = rownames(details)
    
    
    #--------------------
    
    
    
    
    
    while (counter< 30 ){
        file <- paste(folder,"/TSPMap_RandomPoints_Color_SwitchCost_",toString(counter),"-CollectedTour.tspx",sep = "")
        
        counter=counter+1
        fMap <- readLines(file,58)
        #---------------
        tourL = 0
        #-----
        #extracting points and color from each tour file
        matches <- regmatches(fMap, gregexpr("[[:digit:]]+", fMap))
        fN <- as.numeric(unlist(matches))
        fNum<-fN[6:length(fN)]
        coord <- matrix(fNum,byrow = TRUE ,50,3)


        #comparing them with 30maps
        coord_ordered = coord[order(coord[,1])]
        
         res_tbl[counter,1:50] <- coord_ordered[1:50]


  #saving the matched map


    }
        map_order <- 30:59
       
        for (mm in 1:30){
         map_order[mm] <- which(apply(res_tbl_Original, 1, function(x) all(x == res_tbl[mm,1:50])))

         #map_order[mm] <- which(res_tbl_Original==res_tbl_Original[mm,1:50])
         #map_order[mm] <- which(apply(res_tbl_Original[1:30,1:50], 1, function(x) all.equal(x[1:50], res_tbl[mm,1:50])) == "TRUE")
        }
        write(map_order, file = paste(folder,"/rnd.txt",sep = ""))
        ?file     
        
        mode(map_order)
    
}
```

```{r}

```

```{r}

```

```{r}

```

```{r}
#practing exam
years <- 1991 : 2000  # Watch out for: years <- 2000:1991
years
years[] <- 0  # Maintains old vector
years
people <- c("Alice", "Bob", 'Carol') # single/double quotes

class(mean(3))
typeof(mean(3))
mode(mean(3))

years[length(years) + 1] <- 2015
x

vals <- 1 : 3
typeof(vals)

vals[6] <- 6L

print(vals)
length(vals)
?seq

((-2:2) >= 0) && ((-2:10) <= 0)




house <- "Apartment"; 
cat   <- list("Calico", "Flopsy", 3L); 
sofa  <- "Red" 
possessions <- list( house, cat, sofa, "3000USD")

typeof(possessions[[1]])

class(unlist(possessions))
str(possessions)

?setNames





car <- list("Manufacturer" = "Ford", "Make" = "Mustang", 
             "Year" = 1999, "Gasoline" = TRUE )

car[c("Manufacturer", "Make")]  # A two-element sublist
car[["Year"]]   # A length-one vector
car$Year   # Shorthand notation

attributes(car)






my_arr <- array(1 : 8, c(2,2,2)); print(my_arr)


my_mat <- array(1 : 6, c(2,3,1)) # dim(my_mat) is (2,3,1) 
print(my_mat)

my_mat <- drop(my_mat) # dim is now (2,3) 
print(my_mat)



df <- data.frame(age = c(25L,24L,21L),  # Warning: df is an
                 PhD = c( T , T , F ),  #   R function
                 GPA = c(3.6,2.4,2.8))

print(df)
typeof(df)
class(df)


library(tidyverse)
t_mtcars <- as_tibble(mtcars)
class(t_mtcars)

sin_tb <- tibble(x=seq(-5,5,.1), y=sin(x));
print(sin_tb)


grades <- factor(c("a", "a", "b", "f"))
typeof(grades)
levels(grades)
class(grades)

grades <- factor(c("a","a","b","f"),
            levels = c("f","c","b","a"),
            ordered = TRUE )
grades


# First control, then treatment:
gl(2, 8, labels = c("Control", "Treat"))

gl(2, 1, 20) # 20 alternating 1s and 2s
?gl

c(TRUE, TRUE) & c(TRUE, FALSE) & {print("Hello!"); FALSE}



gauss_pdf <- function(ip, mn, vr, lg_pr) {
# Calculate the (log)-probability of Gaussian with mean m and variance vr
  rslt <- -((ip-mn)^2)/(2*vr)
  rslt <- rslt - 0.5*log(2*pi*vr)
# Do we want the prob or the log-prob?
  if(lg_pr == F) rslt <- exp(rslt)
  return(rslt)  
}
str(gauss_pdf)

x <- 5; env <- environment(); env
env$x 









func1 <- function() {my_local <- 1; environment()}
local_env <- func1()
local_env$my_local
parent.env(local_env) # Each environment has a parent environment




x <- 5 
func1 <- function(x) {x + 1}
func1(1)
x <- 5; func2 <- function() {x + 1}
func2(); x
x <- 10; func2() # use new x or x at the time of definition?
x <- 1; y <- 10
func3 <- function() {x <- x + 1; y <<- y + 1; environment()}
env <- func3()
c(x, y, env$x, env$y)
func1 <- function(x) {x + 1}
func4 <- function(x) {func1(x)}
func4(2)
x <- 5; func2 <- function() {x + 1}
func5 <- function(x) {x <- 10; func2()}
func5(2) # func2 uses x from calling or global environment?

func <- function(x,y) if(x) 2*x else x + 2*y
func(1, {print("Hello"); 5})
func(0, {print("Hello"); 5})



mix2norm <- data.frame(dosage = c(rnorm(1000),rnorm(1000,3)),
                     grp = rep(c("a","b"),each=1000))

ggplot(mix2norm, aes(x=dosage, color = grp)) +
    geom_density(adjust=1)


ggplot(mix2norm, aes(x=dosage, color = grp)) + stat_density(adjust=.01)

ggplot(mix2norm, aes(x=dosage, color = grp)) +
  stat_density(adjust=1/2, size=2, position = "jitter",
  geom = "line")



edu_pred <- 10:25
sen_pred <- seq(0,200,10)
pred <- data.frame(Education=rep(edu_pred, length(sen_pred)),
               Seniority=rep(sen_pred, each=length(edu_pred) ))
p_val <- predict.lm(fit, pred)
pred$p_val = p_val


?gather

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
